Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
figures are quite small, but hard to change in a 2-column layout

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{c|c|cc}
            \toprule
            Processor  %& Amount
            &  CPU speed   & \multicolumn{2}{c}{Memory size (GB)} \\
            name & (GHz) & {\em default} & {\em mem-constrained} \\
            \midrule
            local                    & 4                    & 16     & 1.6 \\
            A1                      & 32                   & 32     & 3.2 \\
            A2                      & 6                    & 64    & 6.4 \\
            N1                      & 12                   & 16     & 1.6 \\
            N2                      & 8                    & 8      & 0.8\\
            C2                      & 32                   & 192   &  19.2\\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{Cluster configurations.}
    \label{tab:procs}
\end{table}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
    \caption{Memory usage on default cluster, including only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/makespan_relations_by_wf_size-constrained}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.3cm}
\end{figure}

>>>>

\begin{table}[b]
    \begin{center}
        \begin{tabular}{c|c|cc}
            \toprule
            Processor  %& Amount
            &  CPU speed   & \multicolumn{2}{c}{Memory size (GB)} \\
            name & (GHz) & {\em default} & {\em mem-constrained} \\
            \midrule
            local                    & 4                    & 16     & 1.6 \\
            A1                      & 32                   & 32     & 3.2 \\
            A2                      & 6                    & 64    & 6.4 \\
            N1                      & 12                   & 16     & 1.6 \\
            N2                      & 8                    & 8      & 0.8\\
            C2                      & 32                   & 192   &  19.2\\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{Cluster configurations.}
    \label{tab:procs}
\end{table}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size-constrained}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.3cm}
\end{figure}
